---
title: "Visualization Project Component 1"
author: "Bhumika Dilip Chawla | MDS202215"
output:
  html_document: default
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.height = 4)
```

### Abstract:

The purpose of this project is to analyse various characteristics of
small businesses spread across India. This component of the project
contains some key insights from the data used. Further insights will be
available in the second component of this project.

### Introduction:

The topic for this project is: Analysis of small business owners\
The data used for this project had been collected with the help of a
Google form link without collecting any information that would lead to
respondent's identification.

### Data definition:

The variables present in our data are as follows:

-   Age of the business owner

-   Gender

-   City: The city to which the business owner belongs.

-   Product Category : Decor, Clothing, Home Kitchen etc.

-   Whether the business was established during Covid-19 or prior to it.

-   Number of months since the business has been running.

-   A ranking of Instagram, Facebook, Youtube and WhatsApp as a mode of
    preference for business by the owner.

-   Target audience

-   Shipping range : Whether within state, pan india, international etc.

-   Average Net Profit/month? : (Revenue - Cost)/Revenue \* 100 %\

-   Monthly orders

-   Content interaction

-   Marketing strategy

-   Whether the business owner faces the following constraints:

    -   Budget constraints

    -   Lack of clients\

    -   Lack of inventory\

    -   Shortage of labour\

    -   Family barrier\

    -   Time Constraint\

    -   Place Constraint\

    -   Lack Of Management

-   Capital Investment

-   Mode of delivery

-   Mode of payment

-   Whether registered on other established websites.\

-   Whether the business has a physical store.

-   Whether there is a difference between the profitability from your
    physical and online store.

```{r,include=FALSE}
#Importing, transforming data and defining functions:
library(readxl)
library(dplyr)
library(ggplot2)
dataset = read_excel("C:/Users/HP/OneDrive/Documents/PROJECTS/Analysis of small business owners and customers buying from such businesses/Running A Business.xlsx")


#Convert monthly orders into data types with different categories

datasetnew = dataset %>% 
  mutate(MonthlyOrders = case_when(
    as.numeric(`Monthly orders`) <= 40 ~ '< 40',
    as.numeric(`Monthly orders`) > 40 & as.numeric(`Monthly orders`) <= 80 ~ 'Between 40 - 80',
    as.numeric(`Monthly orders`) > 80 ~ '> 80'
  ))

#Convert shipping range into proper categorical column:
library(dplyr)
Shipping = dataset$`Shipping?`
datasetnew = dataset %>% mutate(Shippingrange = case_when(
    `Shipping?`== "City" ~ 'City',
    `Shipping?` == "Neighbourhood, City" ~ 'City',
    `Shipping` == "City, State" ~ 'Within State',
    `Shipping?` == "Neighbourhood, City, State" ~ 'Within State',
    `Shipping?` == "State" ~ 'Within State',
    `Shipping?` == "International" ~ "International", 
    `Shipping?` == "Neighbourhood, City, State, Pan India, International"  ~ "International",
    `Shipping?` == "Pan India, International" ~ "International",
    `Shipping?` == "Neighbourhood" ~ "Neighbourhood",
    `Shipping?` == "Neighbourhood, City, State, Pan India" ~ 'Pan India',
    `Shipping?` == "Pan India" ~ 'Pan India'
  ))


#convert target audience into proper categorical column:

datasetnew = datasetnew %>%
  mutate(TargetAudience = case_when(
    `Target audience` == "15 - 25 years" ~ '15 to 25 years',
      `Target audience` == "less than 15 years, 15 - 25 years" ~ '< 25 years',
    `Target audience` == "15 - 25 years, 25 - 35 years" ~ '15 to 35 years',
    `Target audience` == "15 - 25 years, 25 - 35 years, 35 - 45 years" ~ '15 to 45 years',
    `Target audience` == "25 - 35 years" ~ "25 to 35 years",
    `Target audience` == "25 - 35 years, 35 - 45 years" ~ '25 to 45 years',
    `Target audience` == "25 - 35 years, 35 - 45 years, more than 45 years" ~ '25 and above',
    `Target audience` == "35 - 45 years" ~ '35 to 45 years',
    `Target audience` == "35 - 45 years, more than 45 years"  ~ '35 and above',
    `Target audience` == "less than 15 years, 15 - 25 years, 25 - 35 years"  ~ '< 35 years',
    `Target audience` == "less than 15 years, 15 - 25 years, 25 - 35 years, 35 - 45 years"  ~ '< 45 years',
    `Target audience` == "less than 15 years, 15 - 25 years, 25 - 35 years, 35 - 45 years, more than 45 years" ~ 'All age groups',
    `Target audience` == "15 - 25 years, 25 - 35 years, 35 - 45 years, more than 45 years" ~ '15 and above'
  ))

#Convert Mode of Delivery into a proper categorical column:

datasetnew = datasetnew%>%
  mutate(ModeofDelivery = case_when(
    `Mode of delivery`== 'Couriers' ~ 'Couriers',
    `Mode of delivery`== "Delivery Partner" |
`Mode of delivery` == "Delivery Partner (BlueDart, Ekart, etc)" ~ "Delivery Partner",
`Mode of delivery` == "Digital media" ~ "Digital media",
`Mode of delivery` == "Indiapost"  ~ "Indiapost" ,
`Mode of delivery` == "NA" ~ "NA",
`Mode of delivery` == "Self Delivery" ~ "Self Delivery",
`Mode of delivery` == "Self Pick-Up" ~ "Self Pick-Up",
`Mode of delivery` == "Staff" ~ "Staff",
`Mode of delivery` == "Wefast Swiggy Uber" ~ "Wefast Swiggy Uber"
))

#Removing inconsistent observation(s):

ind = which(c(datasetnew$`Months of running` > 50 & 
                datasetnew$`Covid, when?` == 'During Covid-19'))

datasetnew = datasetnew[-ind,]



verticalbar = function(dataset,column,rearrange=TRUE)
{
 
  library(ggplot2)
  if(rearrange==TRUE){
  column = factor(column,
                  levels = names(sort(table(column),decreasing=T)))}
  
  ggplot(dataset,aes(x = column,fill=column))+
    geom_bar(show.legend = F,
             aes(y = (..count..)/sum(..count..)))+
    theme_bw()+
    theme(panel.grid.major.x = element_blank())+
    scale_fill_brewer(type = 'qual')
    
}

horizontalbar = function(dataset,column)
{
  library(ggplot2)
  column = factor(column,
                  levels = names(sort(table(column))))
  
  ggplot(dataset,aes(column,fill=column))+
    geom_bar(show.legend = F,
             aes(y = (..count..)/sum(..count..)))+
    theme_bw()+
    theme(panel.grid.major.x = element_blank())+
    scale_fill_brewer(type = 'qual',palette = sample.int(8,1),aesthetics = 'fill') +
    coord_flip()
}

polarchart = function(dataset,column)
{
 
  library(ggplot2)
  ggplot(dataset,aes(column,fill=column))+
    geom_bar(width = 1,colour = 'white')+
    geom_text(stat='count',
aes(y=after_stat(..count..),
    label=after_stat(scales::percent(..count../sum(..count..),1))),
position = position_stack(vjust=0.5))+
    coord_polar()+
    theme_gray()+
    theme(axis.ticks = element_blank(),
          axis.title = element_blank(),
          axis.text = element_blank(),
          axis.line = element_blank())
}

histogram = function(dataset,column)
{
 library(ggplot2)
  ggplot(dataset,aes(column))+
    geom_histogram(bins = 10,fill=sample.int(100,1),color = 'black')+
    theme_bw()+
    theme(panel.grid.major.x = element_blank())
}
scatterplot = function(dataset,col1,col2)
{
 
  library(ggplot2)
  ggplot(dataset,aes(x=col1,y=col2))+
    geom_point(col=sample.int(100,1),size=2) +
    theme_bw()
}

boxplotfn = function(dataset,catv,cont)
{
 
  library(ggplot2)
  ggplot(dataset,aes(x=reorder(catv,cont),y=cont,fill=catv))+
    geom_boxplot(show.legend = F)+
    scale_color_brewer(type='qual',palette = sample.int(8,1),aesthetics = 'fill')+
    theme_bw()
}

stackedbarplotvertical = function(dataset,catv1,catv2)
{

  library(ggplot2)
  ggplot(datasetnew,aes(catv1,
                       fill=catv2))+
    geom_bar(position = 'stack',
             aes(y = (..count..)/sum(..count..))) +
    scale_color_brewer(type='qual',palette = 1,aesthetics = 'fill')+
    theme_bw()+
    theme(panel.grid.major.x = element_blank())
}

stackedbarplothorizontal = function(dataset,catv1,catv2)
{

  library(ggplot2)
  ggplot(datasetnew,aes(catv1,
                       fill=catv2))+
    geom_bar(position = 'stack',
             aes(y = (..count..)/sum(..count..))) +
    coord_flip()+
    scale_color_brewer(type='qual',palette = 1,aesthetics = 'fill')+
    theme_bw()+
    theme(panel.grid.major.x = element_blank())
}
```

### Visualizations:

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.width=4}
p = verticalbar(datasetnew,datasetnew$`Physical store?`) 

p + xlab('Answer')+
  ylab('Proportion') +
  ggtitle('Does the business have physical stores?')+
  theme_bw() + theme(plot.title = element_text(hjust = 0.5))+
  xlim('Yes','No')

```

<br> <br> <br> About **88%** owners in our sample don't have a
physical store and run their business through the internet, basically
they are **E-commerce** businesses. <br> <br> <br> 

```{r,echo=FALSE,message=FALSE,warning=FALSE}
p = histogram(dataset,dataset$`Months of running`)
p+xlab('Months of running') + ylab('Frequency') +
  ggtitle('Distribution of months of running for businesses in our sample.') +
  theme(plot.title = element_text(hjust=0.5))


```

<br> <br> <br> Most of the businesses in our sample have **less**
than **50** **months** of running/ **less** than **5** **years** of
running. <br> <br> <br>

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.width=4}

verticalbar(dataset,dataset$`Covid, when?`) +
  xlim('Prior To Covid-19','During Covid-19') +
  xlab('Lauch period') + ylab('Proportion') +
  ggtitle('When was the business launched?')+
  theme(plot.title = element_text(hjust= 0.5))

```

<br> <br> <br> Most businesses in our data have started their
operation **during** the pandemic of **COVID 19**. <br> <br> <br> 

```{r,echo=FALSE,message=FALSE,warning=FALSE}
polarchart(dataset,dataset$`Product category`) +
  scale_fill_discrete(name = 'Product Category')

```

<br> <br> <br>

* Top 4 product categories in our sample:

    -   Decor

    -   Bakery and chocolate items

    -   Bags and accessories

    -   Clothing

<br> <br> <br> 

```{r,echo=FALSE,message=FALSE,warning=FALSE}

horizontalbar(dataset,dataset$`Seller Instagram`)+
  xlab('Preference') + ylab('Proportion') + 
  ggtitle('Instagram as a preference for business by the owners.')+
  theme(plot.title = element_text(hjust = 0.5))


```

<br> <br> <br> 

**Most** owners in our sample consider **Instagram** to be their **1st**
choice of preference for their business.

<br> <br> <br>

```{r,echo=FALSE,message=FALSE,warning=FALSE}

boxplotfn(datasetnew,datasetnew$`Seller Instagram`,
          datasetnew$`Months of running`) +
  xlim('1st','2nd','3rd','4th') +
  xlab('Instagram ranked as an aid to business.') +    ylab('Age') + 
  ggtitle('Age vs Instagram as a preference')  +
  theme(plot.title = element_text(hjust=0.5))
```

<br> <br> <br> 

```{r,echo=FALSE,message=FALSE,warning=FALSE}
boxplotfn(datasetnew,datasetnew$`Seller Facebook`,
          datasetnew$`Months of running`)+
  xlim('1st','2nd','3rd','4th')+
  xlab('Facebook ranked as an aid to business') +    ylab('Age') + 
  ggtitle('Age vs Facebook as a preference')+
  theme(plot.title = element_text(hjust=0.5))

```

<br> <br> <br> 

We can observe from the 2 graphs above that the businesses which have
**Facebook** as their **1st** platform of preference are **older**
businesses as compared to the businesses which have **Instagram** as
their **1st** platform of preference. Because Instagram has **recently**
started as compared to Facebook and hence the businesses which were
present **long back** use **Facebook** for their business and businesses
which have started **recently** use **Instagram**. <br> <br> <br> 

```{r,echo=FALSE,message=FALSE,warning=FALSE}
boxplotfn(datasetnew,datasetnew$`Covid, when?`,datasetnew$Age)+
  xlim('Prior To Covid-19','During Covid-19')+
  xlab('Launch period of business') +
  ylab('Age of the business owner')+
  ggtitle('Age of business owner vs Launch period of business')+
  theme(plot.title = element_text(hjust=0.5))

```

<br> <br> <br>

Businesses which were established prior to Covid-19 have business owners
with **median** age of **30 years**. While businesses which were
established during Covid-19 have business owners with a median age of
**20 years**, with a **50%** concentration in the age group of **18-24
years**.

<br> <br> <br>

```{r,echo=FALSE,message=FALSE,warning=FALSE}

ggplot(datasetnew,aes(x=`Age`,y=`Months of running`,
                      color=`Covid, when?`))+
geom_point(size=2) + xlab('Age of business owner') +
  labs(color='Lauch Period')  +
  ggtitle('Age of business owner vs Months of running') +
  theme(plot.title = element_text(hjust=0.5))
  
  

```

<br> <br> <br> As expected, owners which are **aged**, own
businesses which have been running for a **longer duration** as compared
to businesses owned by **younger** business owners. <br> <br> <br>

```{r,echo=FALSE,message=FALSE,warning=FALSE}

boxplotfn(datasetnew,datasetnew$`Content interaction`,
          datasetnew$Age) +
  xlim('0-10%','10-20%','20-30%','30-40%','more than 40%')+
  xlab ( 'Percentage of content interaction') +
  ylab('Age of business owner') +
  ggtitle('Age of owner vs the content interaction on various social media websites')

```

<br> <br> <br>The **median** age of the business owners who have
**0-10%** content interaction is **higher** as compared to others who
have **more than 10%** content interaction.

<br>

### Caution:

From the above analysis, we understood that most businesses in our
sample are those which have been launched during the period of Covid-19,
hence there is bias in our sample. Thus any insights drawn from our
sample should not be generalised to the entire population of small
business owners in India.

### Conclusion:

We explored distributions of various variables and their
interrelationships with other variables using univariate and bivariate
plots here. Further exploration of data would be performed in the second
component i.e. the R Shiny Dashboard.
